We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-01-31 paper/paper.tex
edit

The right panel in Figure \ref{fig:scatter_width} shows the result for
the normalized width.  
This panel tells the same story as the middle panel. The M31 values
are typical while the MW is an outlier. 
The added value of the data in this panel is that it is the normalized
which is consistent with normal distributions.
This is the data used to build the mean values vector and covariance
matrix described in Equation \ref{eq:multivariate}.

@@

\subsection{Multivariate Distributions}

This is all the information that is needed to compute the fraction of
pairs that are expected to share the same asphericity as the LG.
We start the Discussion section by describing the results of
performing such a computation.

\section{Discussion}

>>>>

The right panel in Figure \ref{fig:scatter_width} shows the result for
the normalized width.  
This panel tells the same story as the middle panel. The M31 values
are typical while the MW is an outlier. 
The added value of the data in this panel is that it is the normalized
which is consistent with normal distributions.
This is the data used to build the mean values vector and covariance
matrix described in Equation

@@

\subsection{Fit to a Multivariate Gaussian Distributions}

Figure \ref{fig:correlations_illustrisdm} illustrates the results from
 compute the covariance matrix and mean vector in
 Eq.\ref{eq:multivariate} from the normalized quantities in the
 simulation.   
The distributions are computed from $10^6$ with the multivariate
gaussian.

\subsection{Number of Expected LG Systems}
This is all the information that is needed to compute the fraction of
pairs that are expected to share the same asphericity as the LG.
We start the Discussion section by describing the results of
performing such a computation.
